Generality in food webs scales with species richness, not latitude

### 2015-05-18 manuscript/latitudepaper.tex
Need to check a few of these references in my thesis

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for over a century to summarize the structure of 
  ecological communities \citep{Williams2000,earlierwork} and to understand how that structure relates to environmental variables 
  such as land use [[lets really consider the three env variables used here. there really is not a lot of work on land use....i get why prim prod and climate are included....maybe focus on habitat types since you focus on habitats in the analysis]] \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, and climate\citep{}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes \citep{}. [[maybe climatic regimes? the issue is that there really are not a lot of studies that look at these things.....]] These variables affect both the resources available and species' 
  metabolisms~\citep{Stegen2012}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Marquis2005,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,,}.

@@

  If decreased seasonality or higher productivity is the cause of higher species-richness in the tropics, then 
  there should be other effects of latitudinal gradients on food-web structure. Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}[[Check that I don't say that richness causes structural effects elsewhere]]. In particular,
  narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialization may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialization by examining the shape of the scaling 
  relationship between specialization and species richness over changing latitude. Here, we use three measures of specialization:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialization implied by
  the ``latitude-niche breadth hypothesis''.

>>>>

  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
  ecological communities \citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
  such as habitat type \citep{Shurin2006,Briand1983}, primary productivity \citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate\citep{Baiser2012,Petchey2010}. The latter
  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
  climate is more variable at high latitudes \citep{mappaper}. These variables affect both the resources available and species' 
  metabolisms~\citep{,Hechinger2011}, and have been proposed as determinants of the strength of 
  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,Macpherson2002,Kaufman1995}.

@@

  If decreased seasonality or higher productivity is the cause of higher species-richness in the tropics, then 
  there should be other effects of latitudinal gradients on food-web structure. Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. In particular,
  narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialization may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialization by examining the shape of the scaling 
  relationship between specialization and species richness over changing latitude. Here, we use three measures of specialization:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialization implied by
  the ``latitude-niche breadth hypothesis''.
